### 2019-03-20 micro4_2.tex
Micro

			The concept of reactive equilibrium manages to deal with the second problem. This concept allows firms to add more contracts. Then, if we are in the case when separating equilibrium is beaten by pooling, adding another contract (see Fig. \eqref{fig5}, point 2) makes the initial deviation no longer profitable. Hence the separating equilibrium is not beaten by pooling under this concept.
				\begin{figure}[H]
				\centering
				\includegraphics[width=0.8\textwidth]{plotdraft}
				\caption{}\label{fig5}
			\end{figure}
\end{document}

>>>>

			The concept of reactive equilibrium manages to deal with the second problem. This concept allows firms to add more contracts. Then, if we are in the case when separating equilibrium is beaten by pooling, adding another contract (see Fig. \eqref{fig5}, point 2) makes the initial deviation no longer profitable. Hence the separating equilibrium is not beaten by pooling under this concept.
				\begin{figure}[H]
				\centering
				\includegraphics[width=0.8\textwidth]{plotdraft}
				\caption{}\label{fig5}
			\end{figure}

		\section*{7 Single-crossing}
			Most screening models assume single-crossing condition. Think about what this condition
			would require in real life. Do you think single-crossing is always a reasonable assumption?
			Explain why it is reasonable in any application, or suggest a real-life example where this assumption might fail and explain why.

			This condition requires that whatever effort people have already put, for putting the additional amount of effort the low type always requires more compensation than the high type. I think that it is a reasonable assumption in real-life terms but only starting from some point. Some tasks can require extremely low amount of effort, as a result, both groups of people will demand the same amount of compensation for completing these tasks. But starting from some point, tasks become more complicated and require more time and cognitive abilities, in this case people of high type will spend less time, put less effort to solve such a kind of tasks. As a result, it will be cheaper for the company. i.e. high type will require less compensation than the low type, single-crossing condition is satisfied.
\end{document}
